A Detection of the Environmental Dependence of the Stellar Profiles and Halos of Massive Central Galaxies

### 2017-07-10 draft/paper2.tex
Data Reduction 2

    In Paper~I, we select large sample of massive galaxies with either spectroscopic 
    redshift or reliable ``red-sequence'' photometric redshift at $0.3<z<0.5$. 
    Within this redshift range, we have large enough volume to achieve reasonable 
    statistics at very high \mstar{} end, can spatially resolve the inner $\sim 5$ 
    kpc of massive galaxies, and can safely ignore any structural evolution. 
    We derive $i$-band surface brightness profiles out to 100 kpc after carefully 
    masking out any surrounding contaminations and correcting the background 
    subtraction. 
    We measure the average \m2l{} of these galaxies 
    Using the five-band forced \cmodel{} magnitudes from \texttt{hscPipe}, we 
    measure  of the galaxy via SED fitting.

@@

%% ------------------------------------------------------------------------------------ %% 
    Motivated by the two-phase formation scenario, we focus on \mstar{} within two 
    different physical apertures in this work:

        \item The stellar mass within 10 kpc (hereafter noted \minn{}). 
            According to the two-phase scenario, the ``in-situ'' star-formation quickly 
            builds up the inner, dense core of massive ETGs.  
            Based on recent observations and simulations (e.g.~\citealt{vanDokkum2010}; 
            \citealt{RodriguezGomez2016}), the in-situ component of massive ETGs is 
            mostly contained within one effective radius ($R_{\mathrm{e}}$, or 5-10 kpc). 
            We use \minn{} as a proxy for the mass forged during the ``in-situ''
            phase. 
            Given the quality of the HSC data, we can reliably measure \minn{} over our 
            redshift range ($1.0^{\arcsec}$ in radius equals 4.4 and 6.1 kpc at redshift
            0.3 and 0.5).

        \item The stellar mass within 100 kpc (hereafter noted \mtot{}). 
            For our galaxy sample, a 100 kpc aperture corresponds to 5-10 
            $\times R_{\mathrm{e}}$. 
            We show in section \ref{ssec:mtotal} that most of the mass for these ETGs 
            can be captured by a 100 kpc radius and that \mtot{} is a good proxy for the 
            ``total'' \mstar{}. 
            Although not perfect, we argue that our measurements of \mtot{} (which are 
            actually measuring the light directly out to 100 kpc) are a better tracer 
            of total \mstar{} than model-dependent results from shallower data 
            (such as SDSS) which rely on extrapolating the light profiles of galaxies 
            out to large radii.

    {\bf We will show the implications for the stellar mass function of including most of 
    the stellar light, a task that has been complicated before now due to shallower data. 
    We will also investigate the idea that the accreted fraction is a function of stellar mass.}

>>>>

    In Paper~I, we select large sample of massive galaxies with either spectroscopic 
    redshift or reliable ``red-sequence'' photometric redshift (\citealt{Rykoff2014}) 
    at $0.3<z<0.5$. 
    Within this redshift range, we have large enough volume to achieve reasonable 
    statistics at very high \mstar{} end, can spatially resolve the inner $\sim 5$ 
    kpc of massive galaxies ($1.0^{\arcsec}$ corresponds to 4.4 and 6.1 kpc at 
    $z=0.3$ and 0.5), and can safely ignore any structural evolution. 
    We derive $i$-band surface brightness profiles out to 100 kpc after carefully 
    masking out any surrounding contaminations and correcting the background 
    subtraction. 
    We use the broadband spectral energy distributions (SED) fitting code 
    \texttt{iSEDFit}\footnote{http://www.sos.siena.edu/~jmoustakas/isedfit/} 
    (\citealt{Moustakas13}) to measure the average \m2l{} and $k$--correction of 
    these galaxies using five-band forced \cmodel{} magnitudes from \texttt{hscPipe}.
    \citet{Chabrier2003} IMF, Flexible Stellar Population 
    Synthesis\footnote{http://scholar.harvard.edu/cconroy/sps-models}
    (FSPS; \texttt{v2.4}; \citealt{FSPS}, \citealt{Conroy2010}) model, 
    \citet{Calzetti2000} extinction law, simple delayed-$\tau$ model for star 
    formation history (SFH) are assumed here. 
    Using these information, we obtain reliable \mden{} profiles of these 
    galaxies out to $> 100$ kpc and \mstar{} integrated to different physical 
    radius using elliptical apertures.

    As explained in Paper I, here we focus on \mstar{} within

        \item a 10 kpc radii (hereafter noted \minn{}) as proxy of the ``in-situ'' 
            stellar component. 
            This is motivated by recent observations and simulations 
            (e.g.~\citealt{vanDokkum2010}, \citealt{RodriguezGomez2016}).

        \item a 100 kpc radii (hereafter noted \mtot{}), which is shown to recover 
            more \mstar{} than the ones based on \cmodel{} photometry, as proxy of the 
            total \mstar{} of the galaxy.

   \end{itemize}

   Although these radius are empirically selected, they help recover the 
   \mstar{}-dependence of the fraction of accreted stars, and reveal the diversity of 
   stellar envelopes among massive galaxies. 
   In Figure \ref{fig:m100_m10_color}, we demonstrate such diversity by showing 
   a random subsample of massive galaxies with very similar \minn{} that have large 
   range of \mtot{}. 
   We will use these two

%% ------------------------------------------------------------------------------------ %%    
\subsection{Massive Central Galaxies from Different Environment}
    \label{ssec:cen}

@@
